---
title: "p1805_hw1_zo2168"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
colnames(penguins)
distinct(penguins, species)
distinct(penguins,island)
distinct(penguins, sex)
```

```{r max and min of some variables}
max(pull(penguins, bill_length_mm), na.rm = T)
min(pull(penguins, bill_length_mm), na.rm = T)
max(pull(penguins, bill_depth_mm), na.rm = T)
min(pull(penguins, bill_depth_mm), na.rm = T)
max(pull(penguins, flipper_length_mm), na.rm = T)
min(pull(penguins, flipper_length_mm), na.rm = T)
max(pull(penguins, body_mass_g), na.rm = T)
min(pull(penguins, body_mass_g), na.rm = T)
```

```{r}
range(pull(penguins, year),na.rm = T)
nrow(penguins)
ncol(penguins)
```


```{r flipper length mean}
mean(pull(penguins, flipper_length_mm), na.rm = T)
```
The variable names include `species`,`island`,`bill_length_mm`,`bill_depth_mm`,`flipper_length_mm`,`body_mass_g`, `sex`, `year`.\
Three `species` are *Adelie*, *Gentoo*, *Chinstrap*,\
Three `island` are *Torgersen*, *Biscoe*, *Dream*,\
The maximum and minimum of `bill_length_mm` are 59.6 mm and 32.1 mm respectively\
The maximum and minimum of `bill_depth_mm` are 21.5 mm and 13.1 mm respectively\
The maximum and minimum of `flipper_length_mm` are 231 mm and 172 mm respectively\
The maximum and minimum of `body_mass_g` are 6300 and 2700 respectively\
`Year` ranges from 2007 to 2009\
`sex` includes male and female\
This dataset has 344 rows and 8 columns\
Mean flipper length is 200.9152

# Problem 2

I can take the mean of the sample, too! The mean is 
