---
title: "p1805_hw1_zo2168"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
# Problem 1

```{r}
data("penguins", package = "palmerpenguins")
colnames(penguins)
distinct(penguins, species)
distinct(penguins,island)
distinct(penguins, sex)
```

```{r max and min of some variables}
max(pull(penguins, bill_length_mm), na.rm = T)
min(pull(penguins, bill_length_mm), na.rm = T)
max(pull(penguins, bill_depth_mm), na.rm = T)
min(pull(penguins, bill_depth_mm), na.rm = T)
max(pull(penguins, flipper_length_mm), na.rm = T)
min(pull(penguins, flipper_length_mm), na.rm = T)
max(pull(penguins, body_mass_g), na.rm = T)
min(pull(penguins, body_mass_g), na.rm = T)
```

```{r}
range(pull(penguins, year),na.rm = T)
nrow(penguins)
ncol(penguins)
```


```{r flipper length mean}
mean(pull(penguins, flipper_length_mm), na.rm = T)
```
The variable names include `species`,`island`,`bill_length_mm`,`bill_depth_mm`,`flipper_length_mm`,`body_mass_g`, `sex`, `year`.\
Three `species` are *Adelie*, *Gentoo*, *Chinstrap*,\
Three `island` are *Torgersen*, *Biscoe*, *Dream*,\
The maximum and minimum of `bill_length_mm` are 59.6 mm and 32.1 mm respectively\
The maximum and minimum of `bill_depth_mm` are 21.5 mm and 13.1 mm respectively\
The maximum and minimum of `flipper_length_mm` are 231 mm and 172 mm respectively\
The maximum and minimum of `body_mass_g` are 6300 and 2700 respectively\
`Year` ranges from 2007 to 2009\
`sex` includes male and female\
This dataset has 344 rows and 8 columns\
Mean flipper length is 200.9152 is 


```{r}
flipper_vs_bill <- ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) +
  geom_point() +
  labs(x = 'Bill Length (mm)', y = 'Flipper Length (mm)', title = 'Flipper Length vs Bill Length by Species') 
ggsave("flipper_vs_bill_scatterplot.png", plot = flipper_vs_bill, width = 6, height = 4)
```


# Problem 2
```{r}
set.seed(1)
# Create a random sample of size 10 from a standard Normal distribution
std <- rnorm(10)
is.numeric(std)
# Create a logical vector indicating whether elements of the sample are greater than 0
logi <- std > 0
is.logical(logi)
# Create a character vector of length 10
character_vector <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j")
is.character(character_vector)
# Create a factor vector of length 10, with 3 different factor “levels”
factor_index<- sample(0:2, 10, replace = TRUE)
factor_three_levels <- factor(factor_index, labels = c("low","medium","high"))
is.factor(factor_three_levels)
tibble(std,logi,character_vector,factor_three_levels)
```
```{r}
mean(std)
mean(logi)
mean(character_vector)
mean(factor_three_levels)
```
The `charactor_vector` and `factor_three_levels` does not have the mean.  

```{r}
#as.numeric(logi)
#as.numeric(character_vector)
as.numeric((factor_three_levels))

```

It doesn't work for the logistic vector, character vector. But it works for the factor_three_levels